Presentasjon OPX Fiffig tittel

### 2022-08-03 Presentasjon/Presentasjon v3.Rmd
Pres v3
Presentasjon oppdatering

## <br> Phase 1 – how to harvest and analyze the data?
- OPX wanted us to harvest data --> how? <br> 
- A webcrawler? <br> 
- No: Would not work for every organization <br> 
- A code that could read PDF? <br> 
- Perhaps: Financial statements as text tables and as images

@@

- **Which led us to Phase 3 - scrapping the scraping**

@@

## <br> Phase 3 – Scrapping the scraping
- OPX wanted KPIs <br>
- Found useful KPIs <br>
- Created an interactive dashboard

## <br> Data collection & data description
- Used data from OPX and Proff.no <br>
- OPX: From their webpage. <br>
- Used to create KPIs and check our codes <br>
- Proff.no: Downloaded HTML documents. <br>
- Used to create visualizations.

# Findings

# Limitations and steps forward

>>>>

## <br> Phase 1 – how to harvest and analyze the data?
- OPX wanted us to harvest data --> how? <br> 
- A webcrawler? <br> 
No: Would not work for every organization 
- A code that could read PDF? <br> 
Perhaps: Financial statements as text tables and as images

@@

#brns_items
#opx_items

@@

## <br> Which led us to Phase 3 – Scrapping the scraping
- OPX wanted KPIs
- Found useful KPIs
- Created an interactive dashboard

## <br> Data collection & data description
- Used data from OPX and Proff.no 
- OPX: From their webpage
- Used to create KPIs and check our codes
- Proff.no: Downloaded HTML documents
- Used to create visualizations
